%% myCV.tex
%% Copyright 2024 Pini Koplovitch
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License, either version 1.3
% of this license or (at your option) any later version.
%
% This work consists of the files myCVtemplate.cls and myCV.tex.


\documentclass[10pt]{myCVtemplate}
\usepackage{xcolor}

\title{Pini Koplovitch}
\author{Pini Koplovitch}
\name{Pini Koplovitch}
\phone{0528321812}
\email{pini.koplovitch@gmail.com}
\linkedin{pini-koplovitch} 
\github{pinikop}

\def\experience{3}

\begin{document}
    \maketitle

    % A Data Scientist and an Algorithm Developer 
    An Algorithm Developer and a Data Scientist
    with \experience\raisebox{.2ex}{\scriptsize{+}} years' experience in
    % ML \& DL, Computer Vision and Signal Processing,
    Machine \& Deep Learning and Computer Vision,
    extensive research background, proven analytical, learning, and problem-solving skills.
    Experienced with solving algorithmic challenges hands-on and end-to-end. 
    Holds an M.Sc.\ in Computational Neuroscience from the Hebrew University,
    including multiple awards for academic achievement and 2 publications in top journals in the field.
    Looking for exciting Data Science positions, enjoys working in a dynamic and delivery-oriented environment.

    \section{Relevant Experience}{%
        \experienceEntry{Algorithm Developer}{6/2022}{6/2023}{Neteera}{Jerusalem}{}{
            \cvBullet{Led research-to-production development of a Motion-Detection algorithm for patient monitoring from radar signals.}
            \cvBullet{Leveraged Weights\&Biases including Data \& Models Versioning, experiment tracking and visualization; \\introduced the framework to the Algo team, and facilitated adoption for enhanced collaboration.}
            \cvBullet{Crafted ML solutions for Apneas-Detection DL project, implementing modularization and configuration files. This enhanced flexibility in experimenting with alternative components like losses, architectures, metrics and simplified hyperparameter tuning.}
        }
        \experienceEntry{Deep Learning Developer}{4/2021}{4/2022}{Percepto}{Modi'in}{}{
            \cvBullet{Developed DL models for Change-Detection (Segmentation \& Classification) in aerial and static camera images.}
            \cvBullet{Led the migration of TensorFlow-based code to PyTorch ecosystem, optimizing dataloaders, models, and training processes.}
            \cvBullet{Spearheaded the development of synthetic data for training, resulting in a substantial performance enhancement of models.}
            \cvBullet{Monitored and analyzed production models, delivering actionable insights that significantly improved performance.}
        }
        \experienceEntry{Algorithm Developer}{2019}{2020}{Beyond-Sense}{}{}{
            % \cvBullet{End-to-End development of a real-time, DL based Face-Recognition app running on Raspberry Pi.}
            % \cvBullet{Drove the development of a real-time face-recognition app from video on Raspberry Pi, addressing compute power constraints.}
            \cvBullet{Developed a real-time face-recognition app from video on Raspberry Pi, addressing compute power constraints.}
            \cvBullet{Incorporated face detection \& recognition, gender classification, age estimation, \& facial expression analysis into the pipeline.}
            % \cvBullet{Undertook edge device maintenance, overseeing OS installation, source code obfuscation, app installations, \& version updates.}
            \cvBullet{Designed, built and maintained a unique identifier database on the cloud, facilitating seamless updates and communication with both the edge devices and the service backend.}
            % \cvBullet{Led the end-to-end pipeline development, overseeing algorithms on the edge device and in the cloud.}
        }
    }   
    \section{Projects}{
        \experienceEntry{Wounded Skin Segmentation}{2/2020}{7/2020}{}{Healty.io  $\vert$ YData | {\bfseries Distinguished Project}}{}{}{
            \cvBullet{Successfully executed a POC research on skin segmentation from clinical images of patients with chronic wounds.}
            \cvBullet{Achieved performance goals on an extremely scarce dataset by enriching it with external open-source datasets.}
            \cvBullet{Trained and evaluated UNet-based architectures and backbones, optimizing performance and complexity.}
        }{}
    }
    \section{Skills}{
        \skillItemSingle{Programming languages}{Python (PyTorch, TensorFlow, Numpy, OpenCV, Pandas, Scikit), MATLAB}{}
        \skillItemSingle{Technologies}{AWS (EC2, S3), Linux, Git, Weights\&Biases}{}
        \skillItemSingle{Soft skills}{Can work independently or as part of a team, self-learner, project management, tutoring colleagues}{}
    }
    \section{Education}{
        \educationEntry{}{YDATA Program}{Graduated with Honors}
            {2019}{2020}{Yandex advanced Data Science program}{Tel Aviv}{}
        \educationEntry{M.Sc.}{Brain Sciences: Computation and Information Processing}{GPA 96.2}
            {2011}{2016}{The Edmond and Lily Safra Center for Brain Sciences, Hebrew University of Jerusalem}{Jerusalem}
            {Under the supervision of Prof.\ Marshall Devor; Studied the Neuronal Mechanisms of Neuropathic Pain.}
        \educationEntry{B.Sc.}{Cognitive Science; Life Sciences: ``ETGAR'' Honor's Program}{Magna Cum Laude, 94.3}
            {2008}{2010}{The Hebrew University of Jerusalem}{Jerusalem}{}
    }
    \section{Awards and Distinctions}{
        \skillItemSingle{YDATA Industry Project}{completed with outstanding success and honors, chosen for distinction}{2020}
        \skillItemSingle{YDATA Program}{Completed with Distinction and Excellence and Graduated with Honors}{2020}
        \skillItemSingle{B.Sc.}{Graduated with honors | Magna Cum Laude}{2010}
        \skillItemSingle{B.Sc.}{Was on the Dean's list}{2008/9 \& 2009/10}
    }
        
    % \section{Publications}{
    % }

    \section{Languages}{
        \skillItemDouble{Hebrew}{Native speakr}{English}{High level, academic proficiency}
    }


    \recommendations\
\end{document}
